<!-- `r if(knitr:::is_latex_output()) '\\startappendices'` -->

`r if(knitr:::is_latex_output()) '\\appendix'`

<!-- `r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`  -->


# Mathematical details


## Notes on Compound distribution {#chap:appendix-notes-on-compound-distribution}

In section \@ref(chap:nlip-details) we defined the compound distribution (definition \@ref(def:comp-dist)) and we reported some results on it. In this section we report the demonstrations of two results: the characterization of the claim severity $Z$ \@ref(eq:z) and the expected value of the total cost of claims $S$ \@ref(eq:s).


### Characterization of the claim severity $Z$

Let's consider the variabile $Z_i|N\ge i$. We can interpret it as the _claim severity for the $i$^th^ claim under the hypothesis that the $i$^th^ claim occurred_. From the hypotheses provided in definition \@ref(def:comp-dist) we can obtain that also $Z_i|N\ge i$ has the same distribution of $Z_i|N=n, \ i\le n$. This can be easily obtained as follows:

\begin{align}
\label{eq:z1}
P\left(Z_i \le z \middle| N\ge i \right) & = P\left(Z_i \le z \middle| \bigvee_{n = i}^{+\infty}{(N=n)}\right)
\\ \label{eq:z2} & =
\sum_{n=i}^{+\infty}{ \underbrace{P\left(Z_i\le z \middle| N=n\right)}_{=F_Z(z)} P\left( N = n \middle| N\ge i \right)}
\\ \label{eq:z3} & =
\sum_{n=i}^{+\infty}{ F_Z(z) P\left( N = n \middle| N\ge i \right)}
\\ \label{eq:z4} & =
F_Z(z) \underbrace{\sum_{n=i}^{+\infty}{P\left( N = n \middle| N\ge i \right)}}_{=1}
\\ \nonumber & =
F_Z(z)
\end{align}

Where:

* the step \@ref(eq:z1) and the step \@ref(eq:z2) are given by the fact that the event $\{N\ge i\}$ can be decomposed as $\{N\ge i\} = \left\{ \bigvee_{n = i}^{+\infty}{(N=n)} \right\}$ and that the events $\{N=n\}, n\in\{i, i+1, i+2, \dots\}$ are two-by-two disjoint, so they constitute a partition of $\{N\ge i\}$, that allows us to use the disintegrability property of the probability;
* the step \@ref(eq:z3) is due to the fact that the distribution of $Z_i\le z | N=n$ depends neither on $i$ nor on $n$;
* the equivalence $\sum_{n=i}^{+\infty}{P\left( N = n \middle| N\ge i \right)} = 1$ at step \@ref(eq:z4) is due to the fact that the events $\{N=n\}, n\in\{i, i+1, i+2, \dots\}$ are a partition of $\{N\ge i\}$.

This result says that $Z$ can be considered as the _claim severity for a claim under the hypothesis that that claim occurred_.


### Expected value of the total cost of claims $S$

The expected value of the total cost of claims $E(S)$ can be obtained from the expected value of the claims count $E(N)$ and the expected value of the claim severity $E(Z)$ as follows:

\begin{align}
\label{eq:s1}
E(S) & = \sum_{n=0}^{+\infty}{P(N=n) \, E\left(S \middle| N = n \right)}
\\ \label{eq:s2} & =
\sum_{n=0}^{+\infty}{P(N=n) \, E\left(\sum_{i=1}^{n}{Z_i} \middle| N = n \right)}
\\ \label{eq:s3} & =
\sum_{n=0}^{+\infty}{P(N=n) \sum_{i=1}^{n}{\underbrace{E\left( Z_i \middle| N = n \right)}_{=E(Z)}}}
\\ \label{eq:s4} & =
\sum_{n=0}^{+\infty}{P(N=n) n E(Z)}
\\ \label{eq:s5} & =
E(Z) \underbrace{\sum_{n=0}^{+\infty}{n P(N=n)}}_{=E(N)}
\\ \label{eq:s6} & =
E(N)E(Z)
\end{align}

Where:

* the step \@ref(eq:s1) is given by the fact that the events $\{N=0\}, \{N=1\}, \{N=2\}, \dots$ constitute a partition of the certain event $\Omega$, that allows us to use the disintegrability property of the expected value;
* the step \@ref(eq:s2) is due to the definition of $S$;
* the step \@ref(eq:s3) is due to the linearity of the expected value;
* the steps \@ref(eq:s4) and \@ref(eq:s5) are due to the fact that, as assumed by the compound distribution hypotheses, $E\left( Z_i \middle| N = n \right)$ does not depends on $i$ and $n$;
* the step \@ref(eq:s6) is due to the definition of the expected value $E(N)=\sum_{n=0}^{+\infty}{n P(N=n)}$.

This result tells us that, under the hypotheses of the compound distribution, it is possible to easily obtain $E(S)$ from $E(N)$ and $E(Z)$. That means that we can model separately $E(N)$ and $E(Z)$ and, from them, obtain $E(S)$.


\newpage

## Exponential Families {#chap:appendix-exp-family}

In section \@ref(chap:linear-exp-families) we defined the linear exponential family (definition \@ref(def:linear-exp-family)). In this section we report some results on the most used linear exponential families.


### Characterization of exponential families

It can be easily shown that the families Normal, Poisson, Gamma and Binomial are exponential families. In table \@ref(tab:exp-families) the characterizations for these exponential families are reported.

```{r, exp-families-table, echo = FALSE, cache = TRUE}

table <- tibble(
  Distribution = linebreak(c("Normal", "Poisson", "Gamma", "Scaled\nBinomial"),
                           align = "l"),
  # Notation = linebreak(c("$N(\\mu, \\sigma^2)$,\n$\\mu\\in\\mathbb{R}, \\ \\sigma \\in ]0, +\\infty[$",
  #                        "$Poisson(\\mu)$,\n$\\mu \\in ]0, +\\infty[$",
  #                        "$Gamma(\\alpha, \\mu)$,\n$\\alpha \\in ]0, +\\infty[, \\ \\mu \\in ]0, +\\infty[$",
  #                        "$Binom(n, p)/n$,\n$n\\in\\mathbb{N}, \\ p\\in]0,1[$"),
  #                      align = "c"),
  Notation = linebreak(c("$N(\\mu, \\sigma^2)$,\n$\\mu\\in\\mathbb{R}$ \n $\\sigma \\in ]0, +\\infty[$",
                         "$Poisson(\\mu)$,\n$\\mu \\in ]0, +\\infty[$",
                         "$Gamma(\\alpha, \\mu)$,\n$\\alpha \\in ]0, +\\infty[$ \n $\\mu \\in ]0, +\\infty[$",
                         "$Binom(n, p)/n$,\n$n\\in\\mathbb{N}$ \n $p\\in]0,1[$"),
                       align = "c"),
  `$\\Theta$` = c("$\\mathbb{R}$",
                  "$\\mathbb{R}$",
                  "$]-\\infty, 0[$",
                  "$\\mathbb{R}$"),
  `$\\theta$` = c("$\\mu$",
                  "$\\log{(\\mu)}$",
                  "$-\\frac{1}{\\mu}$",
                  "$\\log{\\left(\\frac{p}{1-p}\\right)}$"),
  `$\\Lambda$` = c("$]0, +\\infty[$",
                  "$\\left\\{1\\right\\}$",
                  "$]0,+\\infty[$",
                  "$\\left\\{\\frac{1}{n}\\right\\}$"),
  `$\\lambda$` = c("$\\sigma^2$",
                  "$1$",
                  "$\\frac{1}{\\alpha}$",
                  "$\\frac{1}{n}$"),
  `$b(\\theta)$` = c("$\\frac{\\theta^2}{2}$",
                  "$e^{\\theta}$",
                  "$-\\log{\\left(-\\theta\\right)}$",
                  "$\\log\\left(1+e^{\\theta}\\right)$"),
)


# For compatibility with HTML
if(!knitr::is_latex_output()){
  
  table <- table %>% 
    mutate(
      Distribution = Distribution %>% 
        str_replace_all("\\\\makecell\\[[lrc]\\]\\{(.*)\\}", "\\1") %>% 
        str_replace_all("\\\\\\\\", "<br>"),
      Notation = Notation %>% 
        str_replace_all("\\\\makecell\\[[lrc]\\]\\{(.*)\\}", "\\1") %>% 
        str_replace_all("\\\\\\\\", "<br>"),
    )
  
  names(table) <- names(table) %>% 
    str_replace_all("\\\\makecell\\[[lrc]\\]\\{(.*)\\}", "\\1") %>% 
    str_replace_all("\\\\\\\\", "<br>")
}


table %>% 
  kable(
    format = "latex",
    booktabs = T,
    align = "lcccccc",
    vline = "",
    toprule = "\\toprule",
    # midrule = "\\toprule\\addlinespace",
    midrule = "\\midrule[\\heavyrulewidth]",
    linesep = "\\addlinespace\\hline\\addlinespace",
    bottomrule = "\\bottomrule",
    caption = "Some Linear Exponential Families.",
    label = "exp-families",
    escape = FALSE
  ) %>% 
  kable_styling(
    position = "center",
    latex_options = "hold_position",
    full_width = FALSE
  ) %>% 
  # row_spec(ifelse(!knitr::is_latex_output(), 0, 1), bold = T)
  row_spec(0, bold = T)
  
```


### Canonical link functions

In table \@ref(tab:can-link-fun) the canonical link functions for the families mentioned are reported.

```{r, can-link-fun, echo = FALSE, cache = TRUE}
table <- tibble(
  Distribution = linebreak(c("Normal", "Poisson", "Gamma", "Scaled\nBinomial"),
                           align = "l"),
  `\\makecell[c]{Cumulant function\\\\$b(\\theta)$}` = c("$\\frac{\\theta^2}{2}$",
                     "$e^{\\theta}$",
                     "$-\\log{\\left(-\\theta\\right)}$",
                     "$\\log\\left(1+e^{\\theta}\\right)$"),
  `\\makecell[c]{Derivative\\\\$b'(\\theta)$}` = c("$\\theta$",
                      "$e^\\theta$",
                      "$-\\frac{1}{\\theta}$",
                      "$\\frac{e^{\\theta}}{1 + e^{\\theta}}$"),
  `\\makecell[c]{Canonical link function\\\\$g(\\mu)=b'^{-1}(\\mu)$}` = c("$\\mu$",
                                  "$\\log{(\\mu)}$",
                                  "$-\\frac{1}{\\mu}$",
                                  "$\\log{\\left( \\frac{p}{1-p} \\right)}$"),
)

# For compatibility with HTML
if(!knitr::is_latex_output()){
  
  table <- table %>% 
    mutate(
      Distribution = Distribution %>% 
        str_replace_all("\\\\makecell\\[[lrc]\\]\\{(.*)\\}", "\\1") %>% 
        str_replace_all("\\\\\\\\", "<br>")
    )
  
  names(table) <- names(table) %>% 
    str_replace_all("\\\\makecell\\[[lrc]\\]\\{(.*)\\}", "\\1") %>% 
    str_replace_all("\\\\\\\\", "<br>")
}

table %>% 
  kable(
    # format = "latex",
    booktabs = T,
    align = "lccc",
    vline = "",
    # toprule = "\\toprule",
    # midrule = "\\toprule\\addlinespace",
    # linesep = "\\addlinespace\\hline\\addlinespace",
    # bottomrule = "\\bottomrule",
    toprule = "\\toprule",
    # midrule = "\\toprule\\addlinespace",
    midrule = "\\midrule[\\heavyrulewidth]",
    linesep = "\\addlinespace\\hline\\addlinespace",
    bottomrule = "\\bottomrule",
    caption = "Canonical link functions.",
    label = "can-link-fun",
    escape = FALSE
  ) %>% 
  kable_styling(
    position = "center",
    latex_options = "hold_position",
    full_width = FALSE
  ) %>% 
  # row_spec(ifelse(!knitr::is_latex_output(), 0, 1), bold = T)
  row_spec(0, bold = T)
  
```

In the Gamma case, its canonical function $g(\mu)=-\frac{1}{\mu}$ has the drawback that it links the expected values $\mu\in]0,+\infty[$ to $\eta\in]-\infty, 0[$. This would require some constraints on $\boldsymbol{\beta}$ because $\eta=\boldsymbol{x}^t\boldsymbol{\beta}$ would have to be $<0$. For this reason, it is preferred to use $g(\mu) = \log(\mu)$ that maps $]0, +\infty[$ to $\mathbb{R}$.

In the Scaled Binomial case the canonical function $g(p) = \log{\left(\frac{p}{1-p}\right)}$ is called logit and its inverse $g^{-1}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}$ is called logistic. For the Scaled Binomial distribution we keep using the notation $p$ for the expected value as it corresponds to the probability of success $p$.


### Deviance

In table \@ref(tab:deviance) the deviances for the families mentioned are reported.

```{r, deviance-exp-fam, echo = FALSE, cache = TRUE}
table <- tibble(
  Distribution = linebreak(c("Normal", "Poisson", "Gamma", "Scaled\nBinomial"),
                           align = "l"),
  `Deviance $D(\\hat{\\boldsymbol{\\beta}}, \\boldsymbol{y})$` = c(
    "$\\sum_{i=1}^{n}{\\left( y_i - \\hat{\\mu}_i \\right)^2}$",
    "$2\\,\\sum_{i=1}^{n}{\\left\\{ y_i \\log{\\left(\\frac{y_i}{\\hat{\\mu}_i}\\right)} - \\left( y_i - \\hat{\\mu}_i \\right) \\right\\}}$",
    "$2\\,\\sum_{i=1}^{n}{\\left\\{ - \\log{\\left(\\frac{y_i}{\\hat{\\mu}_i}\\right)} + \\frac{ y_i - \\hat{\\mu}_i }{\\hat{\\mu}_i} \\right\\}}$",
    "$2\\,\\sum_{i=1}^{n}{\\left\\{ y_i \\log{\\left(\\frac{y_i}{\\hat{\\mu}_i}\\right)}+ \\left(1-y_i\\right) \\log{\\left(\\frac{1-y_i}{1-\\hat{\\mu}_i}\\right)} \\right\\}}$"
  ))

# For compatibility with HTML
if(!knitr::is_latex_output()){
  
  table <- table %>% 
    mutate(
      Distribution = Distribution %>% 
        str_replace_all("\\\\makecell\\[[lrc]\\]\\{(.*)\\}", "\\1") %>% 
        str_replace_all("\\\\\\\\", "<br>")
    )
  
  names(table) <- names(table) %>% 
    str_replace_all("\\\\makecell\\[[lrc]\\]\\{(.*)\\}", "\\1") %>% 
    str_replace_all("\\\\\\\\", "<br>")
}

table %>% 
  # mutate_all(
  #   .funs = function(x){
  #     if_else(
  #       knitr::is_latex_output() & (row_number() %% 2 == 1),
  #       str_c("\\cellcolor{gray!6}{", x, "}"),
  #       as.character(x)
  #     )
  #   }
  # ) %>% 
  kable(
    format = "latex",
    booktabs = T,
    align = "lc",
    vline = "",
    toprule = "\\toprule",
    # midrule = "\\toprule\\addlinespace",
    midrule = "\\midrule[\\heavyrulewidth]",
    linesep = "\\addlinespace\\hline\\addlinespace",
    bottomrule = "\\bottomrule",
    caption = "Deviance for Linear Exponential Families.",
    label = "deviance",
    escape = FALSE
  ) %>% 
  kable_styling(
    position = "center",
    latex_options = "hold_position",
    full_width = FALSE
  ) %>% 
  # row_spec(ifelse(!knitr::is_latex_output(), 0, 1), bold = T)
  row_spec(0, bold = T)
```




